|

### 2019-03-17 Paper.Rmd
more paper edits

---
title: |
  | \LARGE{The Effect of Affordable Housing on Neighboring Property Values: }
  | \LARGE{Evidence from San Francisco's Inclusionary Housing Program \vspace{0.5cm}}
author: |
  | Eric Milstein and Tak Hogan
  | Applications of Econometric and Data Science Methods
date: "March 21, 2019"
bibliography: references.bib
output: pdf_document
fontsize: 11pt
fig_caption: yes
indent: true
geometry: margin=1in
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigris)
library(gplots)
library(foreign)
library(car)
library(qwraps2)
library(knitr)
```

@@

###

>>>>

---
title: |
  | \LARGE{The Effect of Affordable Housing on Neighboring Property Values: }
  | \LARGE{Evidence from San Francisco's Inclusionary Housing Program \vspace{0.5cm}}
author: |
  | Eric Milstein and Tak Hogan
  | Applications of Econometric and Data Science Methods
date: "March 21, 2019"
bibliography: references.bib
output: pdf_document
fontsize: 11pt
fig_caption: yes
indent: true
geometry: margin=1in
header-includes:
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \usepackage{float}
- \floatplacement{figure}{H}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
library(tigris)
library(gplots)
library(foreign)
library(car)
library(qwraps2)
library(knitr)
```

@@

![Relative Size of 100m, 200m, 300m Distance Bands on City Map](fig_satellite1.png){width=75%}

![Relative Size of 100m, 200m, 300m Distance Bands around Property](fig_satellite2.png){width=75%}
